Try Bayesian Survival Analysis using the JACC study data (traditional Cox-proportional hazard model presentations)

### 2020-01-12 ForReport20200114/HandOutEng.Rmd

---
title: "Try Bayesian Survival Analysis using the JACC study data"
subtitle: "Tables and figures for analysing the association between milk intake and stroke mortality."
author: "Chaochen Wang | Aichi Medical University"
date: "`r Sys.Date()`"
output:
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
    keep_tex: true
  tufte::tufte_html: default
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
bibliography: skeleton.bib
link-citations: yes
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
---

@@

Before exclusion, we have 110585 participants (46395 men and 64190 women) in the JACC data set:

@@

<!-- Tufte样式在Edward Tufte的书以及物理学家费曼的教科书很常见，它的一个显著特点就是边栏的使用。例如脚注和边栏注解，以及放在边栏里的小型插图。Tufte样式在LaTeX和HTML/CSS中都有实现^[参见Github库[tufte-latex](https://github.com/tufte-latex/tufte-latex)和 [tufte-css](https://github.com/edwardtufte/tufte-css)]。我们将这两种实现都纳入了[**tufte**包](https://github.com/rstudio/tufte)。若需要LaTeX/PDF输出，使用输出格式`tufte_handout`即可，类似地，`tufte_book`可以用来输出PDF书，`tufte_html`生成HTML网页。这些输出格式可以在YAML元数据中指定，或者传给`rmarkdown::render()`函数。若对**rmarkdown**包不熟悉，可参见 @R-rmarkdown。 -->

<!-- ```yaml -->
<!-- --- -->
<!-- title: "一个Tufte样式示例" -->
<!-- author: "张三" -->
<!-- ctex: yes -->
<!-- output: -->
<!--   tufte::tufte_handout: -->
<!--     latex_engine: xelatex -->
<!--   tufte::tufte_html: default -->
<!-- --- -->
<!-- ``` -->

<!-- # 章节标题 -->

<!-- Tufte样式不主张太深的章节目录，一般仅仅使用一级标题（Markdown中用一个井号`#`）和二级标题（两个井号）。 -->

@@

\begin{table}[ht]

@@

\begin{table}[ht]
Table 2. Baseline characteristics of subjects in the JACC study by milk intake level in Women (n = 54,999).

@@

\begin{table}[!h]
Table 3. Sex-specific hazard ratio (95\% CI) of mortality from stroke according to milk intake frequency.

>>>>

---
title: "Try Bayesian Survival Analysis using the JACC study data (traditional Cox-proportional hazard model presentations)"
subtitle: "Tables and figures for analysing the association between milk intake and stroke mortality."
author: "Chaochen Wang | Aichi Medical University"
date: "`r Sys.Date()`"
output:
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
    keep_tex: true
    # includes:  
    #   in_header: preamble-latex.tex
  tufte::tufte_html: default
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
bibliography: skeleton.bib
link-citations: yes
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
---

@@

Before exclusion, we have 110585 participants (46395 men and 64190 women) aged between 40-79 at baseline in the JACC data set:

@@

@@

\begin{table}[!htbp]

@@

\begin{table}[!htbp]
Table 2. Baseline characteristics of subjects in the JACC study by milk intake level in Women (n = 54,999).

@@

\begin{table}[!htbp]
Table 3. Sex-specific hazard ratio (95\% CI) of mortality from stroke according to milk intake frequency.
